LLM Output Compliance with Handcrafted Linguistic Features --- An Experiment

### 2024-07-29 article/main.tex
fix chktex errors

\textbf{Handcrafted linguistic features (HLFs)} are single numerical values
produced by a uniquely identifiable method on any natural
language~\cite{lftk-2023}.
These values are usually easy to compute with methods that are idempotent.
This makes HLFs very attractive because of their dual potential.
They can be used to instruct the generation of text (``write no more than 10
sentences''), but they can also be used to analyse text.
This allows us to verify if a text has the \textit{expected} value for an HLF.

@@

The second scenario consists in generating text based on input text, but with
the aid of some examples from the corpus.
The examples are appended to the instruction prompt used in the first scenario.
The number of examples is chosen so that we do not overrun the context window of
the LLM.
Some context windows are smaller than others, settling the number of examples at
three.
Adding examples to the LLM's instruction prompt also makes the provenance of the
input text more important.
Therefore we experiment with two variants of the second scenario: one with input
text extraneous to the corpus and one with input text from the corpus.
The text from outside the corpus is the same text we used in the first scenario.
The text from within the corpus is chosen randomly once at the start of the
experiment.
Following the process from the first scenario results in obtaining baseline HLF
values for each variant of the second scenario.

@@

The next step requires computing statistics on the corpus for each HLF:
\textbf{min}(the minimum value), \textbf{max}(the maximum value) and
\textbf{avg}(the mean).
These statistics allow writing an HLF prompt derived from each of our baseline
prompts.

@@

\begin{table*}[ht]
    \setlength\tabcolsep{6pt}
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{@{}llllll@{}}
            \toprule
            ID          & Name                    & Parameters  & Context Size & Elo Score & License             \\ \toprule
            gpt         & OpenAI GPT-4o           & undisclosed & 128000       & 1287      & Proprietary         \\
            gemini      & Google Gemini 1.5 Pro   & undisclosed & 1048576      & 1268      & Proprietary         \\
            claude3     & Anthropic Claude 3 Opus & undisclosed & 200000       & 1248      & Proprietary         \\
            llama3\_70b & Meta Llama 3-70B        & 70 Billion  & 8000         & 1208      & Llama 3 Community   \\
            command\_r  & Cohere Command R+       & 104 Billion & 128000       & 1189      & CC-BY-NC 4.0        \\
                        &                         &             &              &           & with Acceptable Use \\
                        &                         &             &              &           & Addendum            \\ \bottomrule
        \end{tabular}%
    }
    \caption{Large Language Model Selection}\label{table-llm}
\end{table*}

@@

The instructions for each HLF are specifically crafted using natural language.
The resulting instructions can be catalogued on the concrete-abstract spectrum.
For example, `write 100 words' is a more concrete instruction than `write as if
you were in junior highschool'.
We divide HLFs in five categories ranging from very concrete to highly abstract
and choose 2 features from each category.
Table~\ref{table-hlf} showcases our selection of features.
The LFTK ID is used throughout tables and figures to refer to a specific HLF.

\begin{table*}[ht]
    \setlength\tabcolsep{6pt}
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{@{}llllll@{}}
            \toprule
            LFTK ID         & Name                              & Family           & Domain           & Abstraction     & Style Level\footnotemark \\ \toprule
            t\_word         & total words                       & wordsent         & surface          & very concrete   & lexical                  \\
            t\_sent         & total sentences                   & wordsent         & surface          & very concrete   & syntactic                \\ \bottomrule
            n\_uverb        & total number of unique adjectives & partofspeech     & syntax           & concrete        & semantic                 \\
            n\_uadj         & total number of unique adjectives & partofspeech     & syntax           & concrete        & syntactic                \\ \bottomrule
            simp\_ttr       & simple type token ratio           & typetokenratio   & lexico-semantics & regular         & pragmatic                \\
            a\_verb\_pw     & number of verbs per word          & partofspeech     & surface          & regular         & syntactic                \\ \bottomrule
            corr\_adj\_var  & corrected adjective variation     & lexicalvariation & lexico-semantics & abstract        & lexical                  \\
            corr\_verb\_var & corrected verb variation          & lexicalvariation & lexico-semantics & abstract        & lexical                  \\ \bottomrule
            fkgl            & Flesch-Kincaid grade level        & readformula      & surface          & highly abstract & pragmatic                \\
            a\_kup\_pw      & Kuperman age of aquisition        & worddiff         & lexico-semantics & highly abstract & lexical                  \\ \bottomrule
        \end{tabular}%
    }
    \caption{Handcrafted Linguistic Features}\label{table-hlf}
\end{table*}
\footnotetext{as described in the figure in~\cite{lugea2023stylistics}, chapter 1, page 7}

@@

We use the Huggingface ecosystem~\cite{lhoest-etal-2021-datasets} to load the
datasets.
Yelp reviews are loaded from \texttt{Yelp/yelp\_review\_full}, while CNN stories
are loaded from \texttt{abisee/cnn\_dailymail}.

@@

We use the two-sampled Kolmogorov-Smirnov~\cite{kolmogorov1933,smirnov1939} test
to determine whether the baseline results are different from the HLF-enhanced
results, as implemented in Scipy~\cite{2020SciPy-NMeth}.
We consider that the results are different for a resulting $p\_value \le 0.05$.

@@

Note that each HLF can have a different range of values than other HLFs.
When we compute the area and the Euclidian norm using Numpy~\cite{harris2020array},
we use the raw values of each HLF, without preprocessing them.
Therefore the results for one HLF are not comparable with the results for
another HLF.
Since we don't quantify how different the baseline is from the result and we
compute the relative closeness to a common target, comparing values for the same
HLF but different LLMs is also ill-advised.

@@

\begin{figure*}[htp]
    \centering
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_1/prompt_1-command_r-cnn_dailymail/prompt_1-command_r-cnn_dailymail_t_word.png}
        \caption{Command-R+\\Total Words}
        \label{fig-command-r-t-word}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_1/prompt_1-gpt-cnn_dailymail/prompt_1-gpt-cnn_dailymail_fkgl.png}
        \caption{GPT\\Flesch-Kincaid Grade Level}
        \label{fig-gpt-fkgl}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_1/prompt_1-claude3-cnn_dailymail/prompt_1-claude3-cnn_dailymail_a_verb_pw.png}
        \caption[center]{Claude3\\Average Verbs per Word}
        \label{fig-llama-simp-ttr}
    \end{minipage}
\end{figure*}

@@

\begin{table*}[hpb]
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{lllllllllll}
            model                 & t\_word                      & t\_sent                    & n\_uverb                    & n\_uadj                    & simp\_ttr                 & a\_verb\_pw               & corr\_adj\_var            & corr\_verb\_var           & fkgl                       & a\_kup\_pw                \\
            \toprule
            claude3 $Diff\_N$     & \textbf{\underline{718.49}}  & \textbf{\underline{24.13}} & \textbf{\underline{44.43}}  & \textbf{\underline{23.43}} & \textbf{\underline{0.4}}  & 0.03                      & 0.94                      & \textbf{\underline{0.77}} & 1.2                        & 0.07                      \\ \midrule
            claude3 $Diff\_A$     & \textbf{\underline{2345.54}} & \textbf{\underline{90.18}} & \textbf{\underline{148.36}} & \textbf{\underline{63.6}}  & \textbf{\underline{1.18}} & 0.07                      & 1.36                      & \textbf{\underline{2.55}} & 3.33                       & 0.52                      \\ \midrule
            gemini $Diff\_N$      & \textbf{\underline{785.6}}   & \textbf{\underline{25.8}}  & \textbf{\underline{60.5}}   & \textbf{\underline{41.6}}  & \textbf{\underline{0.41}} & \textbf{\underline{0.05}} & \textbf{\underline{1.95}} & \textbf{\underline{2.67}} & -4.62                      & \textbf{\textit{-1.94}}   \\ \midrule
            gemini $Diff\_A$      & \textbf{\underline{2512.0}}  & \textbf{\underline{81.5}}  & \textbf{\underline{210.34}} & \textbf{\underline{125.7}} & \textbf{\underline{1.25}} & \textbf{\underline{0.09}} & \textbf{\underline{5.84}} & \textbf{\underline{8.05}} & -9.46                      & \textbf{\textit{-5.82}}   \\ \midrule
            gpt $Diff\_N$         & 47.8                         & 5.18                       & 6.13                        & -0.13                      & 0.02                      & 0.0                       & 0.05                      & 0.3                       & 3.06                       & -0.27                     \\ \midrule
            gpt $Diff\_A$         & 77.0                         & 12.5                       & 13.0                        & -4.0                       & 0.04                      & 0.0                       & -0.17                     & 0.77                      & 8.45                       & -0.16                     \\ \midrule
            command\_r $Diff\_N$  & \textbf{\underline{263.51}}  & 5.35                       & \textbf{\underline{25.08}}  & \textbf{\underline{17.37}} & \textbf{\textit{-0.09}}   & -0.01                     & \textbf{\underline{1.74}} & \textbf{\underline{1.42}} & \textbf{\underline{10.46}} & \textbf{\underline{1.56}} \\ \midrule
            command\_r $Diff\_A$  & \textbf{\underline{896.0}}   & 20.5                       & \textbf{\underline{86.0}}   & \textbf{\underline{60.6}}  & \textbf{\textit{-0.21}}   & -0.03                     & \textbf{\underline{5.45}} & \textbf{\underline{4.95}} & \textbf{\underline{31.29}} & \textbf{\underline{5.67}} \\ \midrule
            llama3\_70b $Diff\_N$ & \textbf{\underline{376.0}}   & \textbf{\underline{15.63}} & \textbf{\underline{38.63}}  & 15.74                      & \textbf{\underline{0.24}} & \textbf{\underline{0.06}} & 1.69                      & \textbf{\underline{2.91}} & 0.31                       & -0.3                      \\ \midrule
            llama3\_70b $Diff\_A$ & \textbf{\underline{1088.5}}  & \textbf{\underline{45.0}}  & \textbf{\underline{113.0}}  & 41.0                       & \textbf{\underline{0.65}} & \textbf{\underline{0.18}} & 3.53                      & \textbf{\underline{8.56}} & 0.27                       & -0.68                     \\ \bottomrule
        \end{tabular}%
    }
    \caption{prompt 2 - CNN Results\\Input Outside Corpus}
    \label{table-prompt-2-cnn-dailymail}
\end{table*}

@@

\begin{figure*}[hpb]
    \centering
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_2/prompt_2-gpt-cnn_dailymail/prompt_2-gpt-cnn_dailymail_t_word.png}
        \caption{GPT\\Total Words}
        \label{fig-p2-gpt-twords}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_2/prompt_2-command_r-cnn_dailymail/prompt_2-command_r-cnn_dailymail_simp_ttr.png}
        \caption{Command-R+\\Simple TTR}
        \label{fig-p2-command-r-simpttr}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_2/prompt_2-gemini-cnn_dailymail/prompt_2-gemini-cnn_dailymail_a_kup_pw.png}
        \caption[center]{Gemini\\Kuperman Age of Aquisition}
        \label{fig-p2-gemini-a-kup-pw}
    \end{minipage}
\end{figure*}

@@

\begin{table*}[ht]
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{lllllllllll}
            model                 & t\_word                      & t\_sent                     & n\_uverb                    & n\_uadj                    & simp\_ttr                 & a\_verb\_pw               & corr\_adj\_var             & corr\_verb\_var            & fkgl                       & a\_kup\_pw              \\
            \toprule
            claude3 $Diff\_N$     & \textbf{\underline{871.02}}  & \textbf{\underline{34.2}}   & \textbf{\underline{34.48}}  & \textbf{\textit{-7.38}}    & \textbf{\underline{0.27}} & 0.01                      & \textbf{\textit{-0.93}}    & \textbf{\textit{-0.72}}    & 1.16                       & -0.14                   \\ \midrule
            claude3 $Diff\_A$     & \textbf{\underline{2756.12}} & \textbf{\underline{117.18}} & \textbf{\underline{126.36}} & \textbf{\textit{-11.2}}    & \textbf{\underline{0.81}} & -0.01                     & \textbf{\textit{-2.52}}    & \textbf{\textit{-0.74}}    & 3.69                       & -0.4                    \\ \midrule
            gemini $Diff\_N$      & \textbf{\underline{1315.41}} & \textbf{\underline{46.19}}  & \textbf{\underline{114.47}} & \textbf{\underline{72.38}} & \textbf{\underline{1.17}} & 0.03                      & \textbf{\underline{5.25}}  & \textbf{\underline{6.64}}  & -1.6                       & \textbf{\textit{-2.1}}  \\ \midrule
            gemini $Diff\_A$      & \textbf{\underline{3996.0}}  & \textbf{\underline{138.0}}  & \textbf{\underline{357.36}} & \textbf{\underline{212.7}} & \textbf{\underline{3.3}}  & 0.06                      & \textbf{\underline{15.49}} & \textbf{\underline{19.4}}  & -13.22                     & \textbf{\textit{-6.19}} \\ \midrule
            gpt $Diff\_N$         & \textbf{\underline{521.29}}  & \textbf{\underline{23.3}}   & \textbf{\underline{43.13}}  & 19.85                      & \textbf{\underline{0.2}}  & 0.02                      & 1.08                       & \textbf{\underline{1.04}}  & 5.09                       & 0.67                    \\ \midrule
            gpt $Diff\_A$         & \textbf{\underline{1464.0}}  & \textbf{\underline{65.5}}   & \textbf{\underline{121.84}} & 58.1                       & \textbf{\underline{0.58}} & 0.05                      & 2.93                       & \textbf{\underline{2.59}}  & 14.23                      & 1.89                    \\ \midrule
            command\_r $Diff\_N$  & \textbf{\underline{371.08}}  & \textbf{\underline{13.31}}  & 22.06                       & \textbf{\underline{17.19}} & \textbf{\underline{0.17}} & \textbf{\underline{0.02}} & 0.88                       & 1.09                       & \textbf{\underline{4.05}}  & -0.15                   \\ \midrule
            command\_r $Diff\_A$  & \textbf{\underline{1198.0}}  & \textbf{\underline{42.5}}   & 73.0                        & \textbf{\underline{56.5}}  & \textbf{\underline{0.69}} & \textbf{\underline{0.07}} & 2.85                       & 3.99                       & \textbf{\underline{13.89}} & -0.11                   \\ \midrule
            llama3\_70b $Diff\_N$ & \textbf{\underline{1040.85}} & \textbf{\underline{41.99}}  & \textbf{\underline{80.58}}  & \textbf{\underline{49.12}} & \textbf{\underline{0.55}} & \textbf{\underline{0.04}} & \textbf{\underline{3.99}}  & \textbf{\underline{5.05}}  & 7.18                       & \textbf{\textit{-1.94}} \\ \midrule
            llama3\_70b $Diff\_A$ & \textbf{\underline{2928.0}}  & \textbf{\underline{118.5}}  & \textbf{\underline{222.0}}  & \textbf{\underline{133.5}} & \textbf{\underline{1.43}} & \textbf{\underline{0.05}} & \textbf{\underline{10.77}} & \textbf{\underline{13.42}} & 17.21                      & \textbf{\textit{-6.2}}  \\ \bottomrule
        \end{tabular}%
    }
    \caption{CNN Results\\Input Inside Corpus}
    \label{table-prompt-2-ifd-cnn-dailymail}
\end{table*}

\begin{figure*}[ht]
    \centering
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_2_ifd/prompt_2-claude3-cnn_dailymail/prompt_2-claude3-cnn_dailymail_n_uadj.png}
        \caption{Claude3\\Number of Unique Adjectives}
        \label{fig-p2-ifd-claude3-nuadj}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_2_ifd/prompt_2-gemini-cnn_dailymail/prompt_2-gemini-cnn_dailymail_t_word.png}
        \caption{Gemini\\Total Words}
        \label{fig-p2-ifd-gemini-twords}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_2_ifd/prompt_2-llama3_70b-cnn_dailymail/prompt_2-llama3_70b-cnn_dailymail_a_kup_pw.png}
        \caption[center]{Llama3\\Kuperman Age of Aquisition}
        \label{fig-p2-ifd-llama3-a-kup-pw}
    \end{minipage}
\end{figure*}

The results in this last scenario show that whether LLMs take examples listed in
the prompt into account is debatable when it comes to generating text with
similar linguistic features as the examples'.

@@

    \caption{Yelp Results - Prompt With Examples\\Input External To Corpus}
    \label{table-prompt-2-yelp}

@@

    \caption{Yelp Results - Prompt With Examples\\Input From Corpus}
    \label{table-prompt-2-ifd-yelp}

>>>>

\textbf{Handcrafted linguistic features (HLFs)} are single numerical values
produced by a uniquely identifiable method on any natural
language~\cite{lftk-2023}.
These values are usually easy to compute with methods that are idempotent.
This makes HLFs very attractive because of their dual potential.
They can be used to instruct the generation of text (``write no more than 10
sentences''), but they can also be used to analyse text.
This allows us to verify if a text has the \textit{expected} value for an HLF.\@

@@

The second scenario consists in generating text based on input text, but with
the aid of some examples from the corpus.
The examples are appended to the instruction prompt used in the first scenario.
The number of examples is chosen so that we do not overrun the context window of
the LLM.\@
Some context windows are smaller than others, settling the number of examples at
three.
Adding examples to the LLM's instruction prompt also makes the provenance of the
input text more important.
Therefore we experiment with two variants of the second scenario: one with input
text extraneous to the corpus and one with input text from the corpus.
The text from outside the corpus is the same text we used in the first scenario.
The text from within the corpus is chosen randomly once at the start of the
experiment.
Following the process from the first scenario results in obtaining baseline HLF
values for each variant of the second scenario.

@@

The next step requires computing statistics on the corpus for each HLF:\@
\textbf{min}\~(the minimum value), \textbf{max}\~(the maximum value) and
\textbf{avg}\~(the mean).
These statistics allow writing an HLF prompt derived from each of our baseline
prompts.

@@

\begin{table*}[ht]
    \setlength\tabcolsep{6pt}
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{@{}llllll@{}}
            \toprule
            ID          & Name                    & Parameters  & Context Size & Elo Score & License             \\ \toprule
            gpt         & OpenAI GPT-4o           & undisclosed & 128000       & 1287      & Proprietary         \\
            gemini      & Google Gemini 1.5 Pro   & undisclosed & 1048576      & 1268      & Proprietary         \\
            claude3     & Anthropic Claude 3 Opus & undisclosed & 200000       & 1248      & Proprietary         \\
            llama3\_70b & Meta Llama 3-{}70B      & 70 Billion  & 8000         & 1208      & Llama 3 Community   \\
            command\_r  & Cohere Command R+       & 104 Billion & 128000       & 1189      & CC-BY-NC 4.0        \\
                        &                         &             &              &           & with Acceptable Use \\
                        &                         &             &              &           & Addendum            \\ \bottomrule
        \end{tabular}%
    }
    \caption{Large Language Model Selection}\label{table-llm}
\end{table*}

@@

The instructions for each HLF are specifically crafted using natural language.
The resulting instructions can be catalogued on the concrete-abstract spectrum.
For example, `write 100 words' is a more concrete instruction than `write as if
you were in junior highschool'.
We divide HLFs in five categories ranging from very concrete to highly abstract
and choose 2 features from each category.
Table~\ref{table-hlf} showcases our selection of features.
The LFTK ID is used throughout tables and figures to refer to a specific HLF.\@

\begin{table*}[ht]
    \setlength\tabcolsep{6pt}
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{@{}llllll@{}}
            \toprule
            LFTK ID         & Name                              & Family           & Domain           & Abstraction     & Style Level\footnotemark\\ \toprule
            t\_word         & total words                       & wordsent         & surface          & very concrete   & lexical                 \\
            t\_sent         & total sentences                   & wordsent         & surface          & very concrete   & syntactic               \\ \bottomrule
            n\_uverb        & total number of unique adjectives & partofspeech     & syntax           & concrete        & semantic                \\
            n\_uadj         & total number of unique adjectives & partofspeech     & syntax           & concrete        & syntactic               \\ \bottomrule
            simp\_ttr       & simple type token ratio           & typetokenratio   & lexico-semantics & regular         & pragmatic               \\
            a\_verb\_pw     & number of verbs per word          & partofspeech     & surface          & regular         & syntactic               \\ \bottomrule
            corr\_adj\_var  & corrected adjective variation     & lexicalvariation & lexico-semantics & abstract        & lexical                 \\
            corr\_verb\_var & corrected verb variation          & lexicalvariation & lexico-semantics & abstract        & lexical                 \\ \bottomrule
            fkgl            & Flesch-Kincaid grade level        & readformula      & surface          & highly abstract & pragmatic               \\
            a\_kup\_pw      & Kuperman age of aquisition        & worddiff         & lexico-semantics & highly abstract & lexical                 \\ \bottomrule
        \end{tabular}%
    }
    \caption{Handcrafted Linguistic Features}\label{table-hlf}
\end{table*}
\footnotetext{as described in the figure in~\cite{lugea2023stylistics}, chapter 1, page 7}

@@

The Huggingface ecosystem~\cite{lhoest-etal-2021-datasets} makes the selected
datasets easily accessible.
Yelp reviews are loaded from \texttt{Yelp/yelp\_review\_full}, while CNN stories
are loaded from \texttt{abisee/cnn\_dailymail}.

@@

Determining whether the baseline results differ from the HLF-enhanced results is
a classic use case for the Kolmogorov-Smirnov~\cite{kolmogorov1933,smirnov1939}
test, as implemented in Scipy~\cite{2020SciPy-NMeth}.
We consider that the results are different for a resulting $p\_value \le 0.05$.

@@

Note that each HLF can have a different range of values than other HLFs.
When we compute the area and the Euclidian norm using Numpy~\cite{harris2020array},
we use the raw values of each HLF, without preprocessing them.
Therefore the results for one HLF are not comparable with the results for
another HLF.\@
Since we don't quantify how different the baseline is from the result and we
compute the relative closeness to a common target, comparing values for the same
HLF but different LLMs is also ill-advised.

@@

\begin{figure*}[htp]
    \centering
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_1/prompt_1-command_r-cnn_dailymail/prompt_1-command_r-cnn_dailymail_t_word.png}
        \caption{Command-R+\\Total Words}\label{fig-command-r-t-word}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_1/prompt_1-gpt-cnn_dailymail/prompt_1-gpt-cnn_dailymail_fkgl.png}
        \caption{GPT\\Flesch-Kincaid Grade Level}\label{fig-gpt-fkgl}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_1/prompt_1-claude3-cnn_dailymail/prompt_1-claude3-cnn_dailymail_a_verb_pw.png}
        \caption[center]{Claude3\\Average Verbs per Word}\label{fig-llama-simp-ttr}
    \end{minipage}
\end{figure*}

@@

\begin{table*}[hpb]
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{lllllllllll}
            model                 & t\_word                      & t\_sent                    & n\_uverb                    & n\_uadj                    & simp\_ttr                 & a\_verb\_pw               & corr\_adj\_var            & corr\_verb\_var           & fkgl                       & a\_kup\_pw                \\
            \toprule
            claude3 $Diff\_N$     & \textbf{\underline{718.49}}  & \textbf{\underline{24.13}} & \textbf{\underline{44.43}}  & \textbf{\underline{23.43}} & \textbf{\underline{0.4}}  & 0.03                      & 0.94                      & \textbf{\underline{0.77}} & 1.2                        & 0.07                      \\ \midrule
            claude3 $Diff\_A$     & \textbf{\underline{2345.54}} & \textbf{\underline{90.18}} & \textbf{\underline{148.36}} & \textbf{\underline{63.6}}  & \textbf{\underline{1.18}} & 0.07                      & 1.36                      & \textbf{\underline{2.55}} & 3.33                       & 0.52                      \\ \midrule
            gemini $Diff\_N$      & \textbf{\underline{785.6}}   & \textbf{\underline{25.8}}  & \textbf{\underline{60.5}}   & \textbf{\underline{41.6}}  & \textbf{\underline{0.41}} & \textbf{\underline{0.05}} & \textbf{\underline{1.95}} & \textbf{\underline{2.67}} & -4.62                      & \textbf{\textit{-1.94}}   \\ \midrule
            gemini $Diff\_A$      & \textbf{\underline{2512.0}}  & \textbf{\underline{81.5}}  & \textbf{\underline{210.34}} & \textbf{\underline{125.7}} & \textbf{\underline{1.25}} & \textbf{\underline{0.09}} & \textbf{\underline{5.84}} & \textbf{\underline{8.05}} & -9.46                      & \textbf{\textit{-5.82}}   \\ \midrule
            gpt $Diff\_N$         & 47.8                         & 5.18                       & 6.13                        & -0.13                      & 0.02                      & 0.0                       & 0.05                      & 0.3                       & 3.06                       & -0.27                     \\ \midrule
            gpt $Diff\_A$         & 77.0                         & 12.5                       & 13.0                        & -4.0                       & 0.04                      & 0.0                       & -0.17                     & 0.77                      & 8.45                       & -0.16                     \\ \midrule
            command\_r $Diff\_N$  & \textbf{\underline{263.51}}  & 5.35                       & \textbf{\underline{25.08}}  & \textbf{\underline{17.37}} & \textbf{\textit{-0.09}}   & -0.01                     & \textbf{\underline{1.74}} & \textbf{\underline{1.42}} & \textbf{\underline{10.46}} & \textbf{\underline{1.56}} \\ \midrule
            command\_r $Diff\_A$  & \textbf{\underline{896.0}}   & 20.5                       & \textbf{\underline{86.0}}   & \textbf{\underline{60.6}}  & \textbf{\textit{-0.21}}   & -0.03                     & \textbf{\underline{5.45}} & \textbf{\underline{4.95}} & \textbf{\underline{31.29}} & \textbf{\underline{5.67}} \\ \midrule
            llama3\_70b $Diff\_N$ & \textbf{\underline{376.0}}   & \textbf{\underline{15.63}} & \textbf{\underline{38.63}}  & 15.74                      & \textbf{\underline{0.24}} & \textbf{\underline{0.06}} & 1.69                      & \textbf{\underline{2.91}} & 0.31                       & -0.3                      \\ \midrule
            llama3\_70b $Diff\_A$ & \textbf{\underline{1088.5}}  & \textbf{\underline{45.0}}  & \textbf{\underline{113.0}}  & 41.0                       & \textbf{\underline{0.65}} & \textbf{\underline{0.18}} & 3.53                      & \textbf{\underline{8.56}} & 0.27                       & -0.68                     \\ \bottomrule
        \end{tabular}%
    }
    \caption{prompt 2 - CNN Results\\Input Outside Corpus}\label{table-prompt-2-cnn-dailymail} % chktex-file 8
\end{table*}

@@

\begin{figure*}[hpb]
    \centering
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_2/prompt_2-gpt-cnn_dailymail/prompt_2-gpt-cnn_dailymail_t_word.png}
        \caption{GPT\\Total Words}\label{fig-p2-gpt-twords}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_2/prompt_2-command_r-cnn_dailymail/prompt_2-command_r-cnn_dailymail_simp_ttr.png}
        \caption{Command-R+\\Simple TTR}\label{fig-p2-command-r-simpttr}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_2/prompt_2-gemini-cnn_dailymail/prompt_2-gemini-cnn_dailymail_a_kup_pw.png}
        \caption[center]{Gemini\\Kuperman Age of Aquisition}\label{fig-p2-gemini-a-kup-pw}
    \end{minipage}
\end{figure*}

@@

\begin{table*}[ht]
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{lllllllllll}
            model                 & t\_word                      & t\_sent                     & n\_uverb                    & n\_uadj                    & simp\_ttr                 & a\_verb\_pw               & corr\_adj\_var             & corr\_verb\_var            & fkgl                       & a\_kup\_pw              \\
            \toprule
            claude3 $Diff\_N$     & \textbf{\underline{871.02}}  & \textbf{\underline{34.2}}   & \textbf{\underline{34.48}}  & \textbf{\textit{-7.38}}    & \textbf{\underline{0.27}} & 0.01                      & \textbf{\textit{-0.93}}    & \textbf{\textit{-0.72}}    & 1.16                       & -0.14                   \\ \midrule
            claude3 $Diff\_A$     & \textbf{\underline{2756.12}} & \textbf{\underline{117.18}} & \textbf{\underline{126.36}} & \textbf{\textit{-11.2}}    & \textbf{\underline{0.81}} & -0.01                     & \textbf{\textit{-2.52}}    & \textbf{\textit{-0.74}}    & 3.69                       & -0.4                    \\ \midrule
            gemini $Diff\_N$      & \textbf{\underline{1315.41}} & \textbf{\underline{46.19}}  & \textbf{\underline{114.47}} & \textbf{\underline{72.38}} & \textbf{\underline{1.17}} & 0.03                      & \textbf{\underline{5.25}}  & \textbf{\underline{6.64}}  & -1.6                       & \textbf{\textit{-2.1}}  \\ \midrule
            gemini $Diff\_A$      & \textbf{\underline{3996.0}}  & \textbf{\underline{138.0}}  & \textbf{\underline{357.36}} & \textbf{\underline{212.7}} & \textbf{\underline{3.3}}  & 0.06                      & \textbf{\underline{15.49}} & \textbf{\underline{19.4}}  & -13.22                     & \textbf{\textit{-6.19}} \\ \midrule
            gpt $Diff\_N$         & \textbf{\underline{521.29}}  & \textbf{\underline{23.3}}   & \textbf{\underline{43.13}}  & 19.85                      & \textbf{\underline{0.2}}  & 0.02                      & 1.08                       & \textbf{\underline{1.04}}  & 5.09                       & 0.67                    \\ \midrule
            gpt $Diff\_A$         & \textbf{\underline{1464.0}}  & \textbf{\underline{65.5}}   & \textbf{\underline{121.84}} & 58.1                       & \textbf{\underline{0.58}} & 0.05                      & 2.93                       & \textbf{\underline{2.59}}  & 14.23                      & 1.89                    \\ \midrule
            command\_r $Diff\_N$  & \textbf{\underline{371.08}}  & \textbf{\underline{13.31}}  & 22.06                       & \textbf{\underline{17.19}} & \textbf{\underline{0.17}} & \textbf{\underline{0.02}} & 0.88                       & 1.09                       & \textbf{\underline{4.05}}  & -0.15                   \\ \midrule
            command\_r $Diff\_A$  & \textbf{\underline{1198.0}}  & \textbf{\underline{42.5}}   & 73.0                        & \textbf{\underline{56.5}}  & \textbf{\underline{0.69}} & \textbf{\underline{0.07}} & 2.85                       & 3.99                       & \textbf{\underline{13.89}} & -0.11                   \\ \midrule
            llama3\_70b $Diff\_N$ & \textbf{\underline{1040.85}} & \textbf{\underline{41.99}}  & \textbf{\underline{80.58}}  & \textbf{\underline{49.12}} & \textbf{\underline{0.55}} & \textbf{\underline{0.04}} & \textbf{\underline{3.99}}  & \textbf{\underline{5.05}}  & 7.18                       & \textbf{\textit{-1.94}} \\ \midrule
            llama3\_70b $Diff\_A$ & \textbf{\underline{2928.0}}  & \textbf{\underline{118.5}}  & \textbf{\underline{222.0}}  & \textbf{\underline{133.5}} & \textbf{\underline{1.43}} & \textbf{\underline{0.05}} & \textbf{\underline{10.77}} & \textbf{\underline{13.42}} & 17.21                      & \textbf{\textit{-6.2}}  \\ \bottomrule
        \end{tabular}%
    }
    \caption{CNN Results\\Input Inside Corpus}\label{table-prompt-2-ifd-cnn-dailymail}
\end{table*}

\begin{figure*}[ht]
    \centering
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_2_ifd/prompt_2-claude3-cnn_dailymail/prompt_2-claude3-cnn_dailymail_n_uadj.png}
        \caption{Claude3\\Number of Unique Adjectives}\label{fig-p2-ifd-claude3-nuadj}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_2_ifd/prompt_2-gemini-cnn_dailymail/prompt_2-gemini-cnn_dailymail_t_word.png}
        \caption{Gemini\\Total Words}\label{fig-p2-ifd-gemini-twords}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_2_ifd/prompt_2-llama3_70b-cnn_dailymail/prompt_2-llama3_70b-cnn_dailymail_a_kup_pw.png}
        \caption[center]{Llama3\\Kuperman Age of Aquisition}\label{fig-p2-ifd-llama3-a-kup-pw}
    \end{minipage}
\end{figure*}

The outcomes from the latest experiment are ambiguous. The LLMs do not seem to
utilize the examples given in the prompt to their advantage when they generate
text that should mirror the linguistic features of those examples.

@@

    \caption{Yelp Results - Prompt With Examples\\Input External To Corpus}\label{table-prompt-2-yelp}

@@

    \caption{Yelp Results - Prompt With Examples\\Input From Corpus}\label{table-prompt-2-ifd-yelp}
